Trends of downward SDR in Thessaloniki

### 2023-05-06 Article.Rmd
Commit 2023-05-06 10:17

```{r cm, echo=F, fig.cap="Donditions."}
knitr::include_graphics("./images/CumulativeDailyCumSum-1.pdf")
```

>>>>

```{r cumsumALL, echo=F, fig.cap="Donditions."}
knitr::include_graphics("./images/CumulativeDailyCumSum-1.pdf")
```

```{r cumsumCLEAR, echo=F, fig.cap="Donditions."}
knitr::include_graphics("./images/CumulativeDailyCumSum-5.pdf")
```

```{r cumsumCLOUD, echo=F, fig.cap="Donditions."}
knitr::include_graphics("./images/CumulativeDailyCumSum-9.pdf")
```
